Argennon: A Scalable Smart Contract Platform

### 2021-04-28 tex/sections/blockchain.tex
Do minor modification
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\begin{center}
    \begin{tabular}{||c||}
        \hline
        \textbf{Block} \\ [0.5ex]
        \hline\hline
        commitment to the staking database \\ [0.7ex]
        commitment to the method database \\ [0.7ex]
        commitment to the heap database \\ [0.7ex]
        commitment to the set of transactions       \\ [0.7ex]
        previous block hash                         \\ [0.7ex]
        random seed                                 \\ [0.7ex]
        \hline
    \end{tabular}
\end{center}

>>>>

\begin{center}
    \begin{tabular}{||c||}
        \hline
        \textbf{Block} \\ [0.5ex]
        \hline\hline
        commitment to the staking database      \\ [0.7ex]
        commitment to the method database       \\ [0.7ex]
        commitment to the heap database         \\ [0.7ex]
        commitment to the set of transactions   \\ [0.7ex]
        clustering directives                   \\ [0.7ex]
        previous block hash                     \\ [0.7ex]
        random seed                             \\ [0.7ex]
        \hline
    \end{tabular}
\end{center}

### 2021-04-28 tex/sections/concurrency.tex
Do minor modification
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

%##\includegraphics[width=17cm]{../img/Alg1s.png}
\begin{algorithm}
    \DontPrintSemicolon
    \SetKwData{Ready}{$R_e$}\SetKwData{V}{$v_f$}\SetKwData{Graph}{$G_e$}\SetKwData{Vertices}{$V$}\SetKwData
    {Txns}{$T$}
    \KwData{The execution dag $\Graph = (\Vertices,E)$ of transaction set \Txns}
    \KwResult{The state of the AVM after applying \Txns with any ordering respecting \Graph}
    \BlankLine
    \Ready $\gets$ the set of all vertices of \Vertices with in degree 0\;
    \While{$\Vertices \neq \varnothing$}
    {
        wait until a new free processor is available\;
        \If{the execution of a transaction was finished}
        {
            remove the vertex of the finished transaction \V from \Graph\;
            \For{each vertex $u \in Adj[\V]$}
            {
                \If{$u$ has zero in degree}
                {
                    $\Ready \gets \Ready \cup u$\;
                }
            }
        }
        \If{$\Ready \neq \varnothing$}
        {
            remove a vertex from \Ready and assign it to a processor\;
        }
    }
    \caption{executing DAG transactions}\label{alg:exec_dag}
\end{algorithm}

@@

\subsection{Memory Chunks}\label{subsec:memory-chunks}

In order to further increase the concurrency level of Argennon, we can divide the AVM memory into \emph{chunks}.
Each memory chunk can be persisted using a different ZK-EDB, hence having its own commitment. Then, the
consensus on new values of the commitment of any chunk can be achieved by a different voting committee.

If a transaction does not modify a memory chunk and in the transaction ordering of the block it comes after
any transaction which modifies that chunk, then the execution of that transaction is not needed for calculating
the new commitment of the chunk. Consequently, the voting committee of that memory chunk can safely ignore such a
transaction. The execution DAG of transactions can be used for finding and pruning these transactions as
we see in Algorithm~\ref{alg:prune_dag}.

%##\includegraphics[width=17cm]{../img/Alg4s.png}
\begin{algorithm}
    \DontPrintSemicolon
    \SetKwData{V}{$v_0$}\SetKwData{Graph}{$G_e$}\SetKwData{Chunk}{$C_k$}\SetKwData{Txns}{$T$}
    \SetKwFunction{RPrune}{RecursivePrune}
    \SetKwProg{Fn}{Function}{}{}
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
    \Input{An execution dag \Graph and a memory chunk \Chunk}
    \Output{The pruned execution dag based on \Chunk}
    \BlankLine
    \For{each vertex \V with out degree $0$}
    {
        \RPrune{\V}\;
    }
    \BlankLine
    \Fn{\RPrune{\V}}
    {
        \If{$Adj[\V] = \varnothing$ {\bf and} \V does not modify \Chunk}
        {
            remove \V from \Graph\;
            \For{each $u$ such that edge $(u,\V)$ was in \Graph}
            {
                \RPrune{u}\;
            }
        }
    }
    \caption{Pruning an execution DAG}\label{alg:prune_dag}
\end{algorithm}

If we choose chunks in a way that most transactions only modify memory locations of one chunk,
likely many transactions of a block only need to be validated by one voting committee and can be validated in
parallel by different committees.

>>>>

%##\includegraphics[width=17cm]{../img/Alg1s.png}
\begin{algorithm}
    \DontPrintSemicolon
    \SetKwData{Ready}{$R_e$}\SetKwData{V}{$v_f$}\SetKwData{Graph}{$G_e$}\SetKwData{Vertices}{$V$}\SetKwData
    {Txns}{$T$}
    \KwData{The execution dag $\Graph = (\Vertices,E)$ of transaction set \Txns}
    \KwResult{The state of the AVM after applying \Txns with any ordering respecting \Graph}
    \BlankLine
    \Ready $\gets$ the set of all vertices of \Vertices with in degree 0\;
    \While{$\Vertices \neq \varnothing$}
    {
        wait until a new free processor is available\;
        \If{the execution of a transaction was finished}
        {
            remove the vertex of the finished transaction \V from \Graph\;
            \For{each vertex $u \in Adj[\V]$}
            {
                \If{$u$ has zero in degree}
                {
                    $\Ready \gets \Ready \cup u$\;
                }
            }
        }
        \If{$\Ready \neq \varnothing$}
        {
            remove a vertex from \Ready and assign it to a processor\;
        }
    }
    \caption{Executing DAG transactions}\label{alg:exec_dag}
\end{algorithm}

@@

\subsection{Memory Shards}\label{subsec:memory-shards}

In order to further increase the concurrency level of Argennon, we can divide the AVM memory into \emph{shards}.
Each memory shard can be persisted using a different ZK-EDB, hence having its own commitment. Then, the
consensus on new values of the commitment of any shard can be achieved by a different voting committee.

If a transaction does not modify a memory shard and in the transaction ordering of the block it comes after
any transaction which modifies that shard, then the execution of that transaction is not needed for calculating
the new commitment of the shard. Consequently, the voting committee of that memory shard can safely ignore such a
transaction. The execution DAG of transactions can be used for finding and pruning these transactions as
we see in Algorithm~\ref{alg:prune_dag}.

%##\includegraphics[width=17cm]{../img/Alg4s.png}
\begin{algorithm}
    \DontPrintSemicolon
    \SetKwData{V}{$v_0$}\SetKwData{Graph}{$G_e$}\SetKwData{Shard}{$Sh_k$}\SetKwData{Txns}{$T$}
    \SetKwFunction{RPrune}{RecursivePrune}
    \SetKwProg{Fn}{Function}{}{}
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
    \Input{An execution dag \Graph and a memory shard \Shard}
    \Output{The pruned execution dag based on \Shard}
    \BlankLine
    \For{each vertex \V with out degree $0$}
    {
        \RPrune{\V}\;
    }
    \BlankLine
    \Fn{\RPrune{\V}}
    {
        \If{$Adj[\V] = \varnothing$ {\bf and} \V does not modify \Shard}
        {
            remove \V from \Graph\;
            \For{each $u$ such that edge $(u,\V)$ was in \Graph}
            {
                \RPrune{u}\;
            }
        }
    }
    \caption{Pruning an execution DAG}\label{alg:prune_dag}
\end{algorithm}

If we choose shards in a way that most transactions only modify memory locations of one shard,
likely many transactions of a block only need to be validated by one voting committee and can be validated in
parallel by different committees.

### 2021-04-28 tex/sections/persistence.tex
Update the rest of the document
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Do minor modification
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon Virtual Machine has two persistent memory areas: \emph{method area}, and \emph{heap}. Method area stores
method byte codes \footnote{also it stores constant area blocks.}, and heap stores memory chunks. Both of these
data elements, methods and chunks, can be considered as continuous pieces of byte addressable memory
which we shall call \emph{objects} throughout this chapter.

In the AVM persistence layer, similar objects are clustered together and constitute a bigger data element which we call a
\emph{page}.\footnote{we avoided calling them a cluster, because usually a cluster refers to a \emph{set}. AVM object
clusters are not sets. They are ordered lists, like a page containing an ordered list of words or sentences.}
A page is an ordered list of an arbitrary number of objects, which their order reflects the order they were added to
the page:
\[
    P = (O_1,O_2,\dots,O_n),\quad i < j \; \Leftrightarrow \; \textrm{$O_i$ was added before $O_j$}
\]

A page of the AVM storage should contain objects that have very similar access pattern. We expect that when a page
is needed for validating a block, almost all of its objects are needed. We also prefer that the objects of the page
are needed for the same access type. In other words, the objects of a page are chosen in a way that
for validating a block, we usually need to either read all of them or modify\footnote{and probably read.} all of them.

Pages of the AVM storage space are persisted using updatable zero-knowledge elementary databases (ZK-EDB). Argennon
has three zero-knowledge databases. \emph{Staking} database which stores all the data that is associated with
the Argennon agreement protocol. \emph{Method} database which stores the AVM method area, and \emph{Heap} database which
stores the AVM heap. The commitment of these three ZK-EDBs are included in every block of the Argennon blockchain.

@@

The commitments of the AVM databases are dependant to the clustering of data objects. So, the clustering algorithm of
the AVM storage has to be a part of the Argennon agreement protocol. Clustering of objects is one of the
tasks that a block proposer performs in Argennon.

@@

A block proposer usually obtains clustering directives from a third party source who enjoys a considerable amount of
computational power. This federated approach does not affect Argennon security, because the integrity of a
database can not be altered by clustering directives. Those
directives can only affect the performance of the argennon blockchain, and directives of a single block can
not change the performance much.

>>>>

The Argennon Virtual Machine has two persistent memory areas: \emph{method area}, and \emph{heap}. Method area stores
method byte codes\footnote{also it stores constant area blocks.}, and heap stores memory chunks. Both of these
data elements, methods and chunks, can be considered as continuous pieces of byte addressable memory
which we shall call \emph{objects} throughout this chapter.

In the AVM persistence layer, similar objects are clustered together and constitute a bigger data element which we call a
\emph{page}.\footnote{we avoided calling them clusters, because usually a cluster refers to a \emph{set}. AVM object
clusters are not sets. They are ordered lists, like a page containing an ordered list of words or sentences.}
A page is an ordered list of an arbitrary number of objects, which their order reflects the order they were added to
the page:
\[
    P = (O_1,O_2,\dots,O_n),\quad i < j \; \Leftrightarrow \; \textrm{$O_i$ was added before $O_j$}
\]

A page of the AVM storage should contain objects that have very similar access pattern. We expect that when a page
is needed for validating a block, almost all of its objects are needed. We also prefer that the objects
are needed for the same access type. In other words, the objects of a page are chosen in a way that
for validating a block, we usually need to either read all of them or modify\footnote{and probably read.} all of them.

Pages of the AVM storage space are persisted using updatable zero-knowledge elementary databases (ZK-EDB). Argennon
has three zero-knowledge databases. \emph{staking} database, which stores all the data that is associated with
the Argennon agreement protocol. \emph{method} database, which stores the AVM method area, and \emph{heap} database,
which stores the AVM heap. The commitment of these three ZK-EDBs are included in every block of the Argennon blockchain.

@@

The commitments of the AVM databases are dependant to the shape of clusters of data objects. So,
the clustering algorithm of the AVM storage has to be a part of the Argennon agreement protocol. Clustering of
objects is one of the tasks that a block proposer performs in Argennon.

@@

A block proposer usually obtains clustering directives from a third party source who enjoys a considerable amount of
computational power.\footnote{we can say the AVM clustering algorithm is essentially off-chain.} This federated approach
does not affect Argennon security, because the integrity of a database can not be altered by clustering directives.
Those directives can only affect the performance of the argennon blockchain, and directives of a single block can
not change the performance much.
